A Non-Modal Analytical Method to Predict Turbulent Properties Applied to the Hasegawa-Wakatani Model

### 2014-12-26 Referee_Responses/referee_response.tex

{\bf Response to Referees \\
 \\} 
Brett Friedman and Troy Carter
%Updated: \today \\

\hrulefill

We would like to thank the referee for his/her thorough reading of our paper and clear and insightful comments. We have responded to each comment below and made requisite changes to the text.
Most of the changes are relatively minor and involve corrections pointed out by the referee, changes in wording, and further clarification on certain points.

The referee's comment 14 is a rather significant one, suggesting the possible removal of Section V of the paper. 
We agree with the points but don't want to go so far as to remove the entire section because even though the result is weak (unsuccessful), 
we believe that it is still valuable and provides some important insight. What we have done, then, is move it to an appendix. 
We have also adjusted the title, abstract, and introduction to de-emphasize that part of the paper. \\ \\

@@

\emph{11) Eq. 21 misses a factor 1/2 }\\

We had meant to define $u_k = 1/ \sqrt{2} (n_k, k \phi_k)^T$ so that the factor of $1/2$ wasn't necessary, but we missed the $\sqrt{2}$ factor in an earlier expression, so that was the incorrect one.\\

\emph{12) On Eq. 22. There is an unspelled assumption here on the distribution of the ensemble. Are all states equally distributed? Is such distribution physical meaningful? Also, I would emphasize the fact that by averaging over an ensemble of states, the information about the initial condition is lost (or averaged out). This is a crucial point because one of the main weaknesses of non-modal analysis with respect to the standard normal mode analysis, is the need to specify a given initial condition. }\\

Yes all states are equally distributed initially. Remember that each state at a particular $k$ is completely classified by the ratio $n_k/\phi_k$ as far as the growth rate is concerned.
So each member of the ensemble is initially one possible value of this complex ratio. But once the initial states have evolved under the linear operator for some time, not all of
the possible values of the ratio are populated. In fact, after a long enough time, this ratio is nearly equal to that of the faster growing eigenmode for all members of the ensemble.
The time average, then, produces something meaningful -- that is, an average over many ratios between a random ratio and the eigenmode ratio.
